\documentclass[conference]{IEEEtran}
% \IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
%Template version as of 6/27/2024

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
% \usepackage{hyperref}
\usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\newcommand{\nsnote}[1] {{$\langle${\textcolor{blue}{NS: \textbf{#1}}}$\rangle$}}
\begin{document}

\title{Scalable Federated Fusion Planning for Decentralized Satellite-Based Ground Tracking\\
}

\author{\IEEEauthorblockN{ Nolan Stevenson}
\IEEEauthorblockA{\textit{ASEN 6519: Optimization: Applications and Algorithms} \\
\textit{University of Colorado Boulder} \\
}
}

\maketitle

\begin{enumerate}
    \item \href{https://github.com/nolans12/Satellite-DDF}{{\textcolor{blue}{Link to GitHub repository here.}}}
    \item \href{https://youtu.be/t9Bo5KCvhZA}{{\textcolor{blue}{Link to video here.}}}
\end{enumerate}

\input{body/1_introduction}

\input{body/2_background}

\input{body/3_problem}

\input{body/4_solution}

\input{body/5_results}

\input{body/6_conclusion}

\input{body/7_contributions}

\input{body/8_additional_figures}
\begin{thebibliography}{00}

\bibitem{b1} M. E. Campbell and N. R. Ahmed, "Distributed Data Fusion: Neighbors, Rumors, and the Art of Collective Knowledge," IEEE Control Systems Magazine, vol. 36, no. 4, pp. 83-109, Aug. 2016.
\bibitem{b2} COIN-OR: Computational Infrastructure for Operations Research, "COIN-OR: Computational Infrastructure for Operations Research," 2024. [Online].
\bibitem{b3} "Decentralized Task Allocation Using Local Information Consistency Assumptions," Journal of Information Systems, 2024.
\bibitem{b4} R. Forsling, B. Noack, and G. Hendeby, "A Quarter Century of Covariance Intersection: Correlations Still Unknown? [Lecture Notes]," IEEE Control Systems Magazine, vol. 44, no. 2, pp. 81-105, Apr. 2024.
\bibitem{b5} S. J. Julier and J. K. Uhlmann, "A New Extension of the Kalman Filter to Nonlinear Systems," in Proc. SPIE 3068, Signal Processing, Sensor Fusion, and Target Recognition VI, 1997.
\bibitem{b6} S. Mitchell, M. O'Sullivan, and I. Dunning, "PuLP: A Linear Programming Toolkit for Python," The Python Papers, vol. 3, no. 1, 2011.
\bibitem{b7} H. Nabli, "An Overview on the Simplex Algorithm," Applied Mathematics and Computation, vol. 210, no. 2, pp. 479-489, Apr. 2009.
\bibitem{b8} R. T. Rockafellar and S. Uryasev, "Optimization of Conditional Value-at-Risk," The Journal of Risk, vol. 2, no. 3, pp. 21-41, 2000.
\bibitem{b9} W. J. Thompson, "Poisson Distributions," Computing in Science and Engineering, vol. 3, no. 3, pp. 78-82, May 2001.
\bibitem{b10} B. E. White, "Tactical Data Links, Air Traffic Management, and Software Programmable Radios," in 18th Digital Avionics Systems Conference Proceedings, St Louis, MO, 1999, pp. 5.C.5-1-5.C.5-8.

\end{thebibliography}

\end{document}
